---
output: github_document
header-includes:
  - \usepackage{color}
  - \usepackage{amsmath}
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Build Status](https://travis-ci.com/dazamora/IDFtool.svg?branch=master)](https://travis-ci.com/dazamora/IDFtool)
[![codecov](https://codecov.io/gh/dazamora/IDFtool/branch/master/graph/badge.svg)](https://codecov.io/gh/dazamora/IDFtool)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  out.width = "100%"
)
```
# IDFtool
IDFtool computes intensity-duration-frequency curves per specific time duration and different return periods. The intensity-duration-frequency curves are used in hydrology to express in a synthetic way, fixed a return period (T) and a duration (d) of a rainfall event. IDFtool included an uncertainty analysis in PDFs and IDF curves, by bootstrap method.

## Instalation
Currently, you can install the version under development from [Github](https://github.com/dazamora/IDFtool), using these commands:

```{r eval=FALSE, include=TRUE}
install.packages("devtools")
devtools::install_github("dazamora/IDFtool")
```

## Example
Meteorology station in the Farfan Airport in Tulua, Colombia.
```{r fig.align= "center", fig.height=4, fig.width=6, dpi = 300}
library(IDFtool)
data(inten)
Test.idftool <- IDFCurve(Data = inten, Station='2610516', Duration = FALSE,
                         Periods = FALSE, Type = "gumbel", M.fit = "lmoments",
                         Plot = 1234, Strategy = 1, logaxe = "", CI = FALSE, 
                         CIpdf = TRUE, iter = 50, goodtest = FALSE,
                         Resolution = 300, SAVE = FALSE, name = TRUE)
```

